---
title: "Introduction to Quarto"
format: html
bibliography: references.bib
---

Markdown formatting

# This is a large title

## this is a smaller title

###### this is an even smaller title

*text* **bold**

-   Item 1
-   Item 2
    -   Item 2a
    -   Item 2b

1.  Item 1
2.  Item 2
3.  Item 3
    -   Item 3a
    -   Item 3b

Roses are red,\
Violets are blue.

hold on wait a minute[@oke2020]

| Col1          | Col2 |
|---------------|------|
| hello         | 1    |
| wait a minute | 2    |

# Introduction

## About the data

-Water sample data from Arctic Ocean -Data downloaded from the Arctic Data Center: [Tweedie ADC data](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)

## Setup

```{r}
#| warning: false
library(readr)
library(here)
```

## Read in data

```{r}
#| warning: false
bg_chem<-read_csv(here("data/BGchem2008data.csv"))
#here() looks into home directory to get file and makes it so that you don't have to specify a personal working directory
```

# Analysis 
## a. Calculate summary statistics

```{r}
#| eval: false
#| echo: false
#Print column names
colnames(bg_chem)
#Show data structure
str(bg_chem)
#Show first 6 lines of data frame
head(bg_chem)
#Get summary of each column
summary(bg_chem)
#Print unique values in a specific column
unique(bg_chem$Date)

```

## b.Calculate mean Redfield ratio
```{r}
nitrate<-mean(bg_chem$NO3)
nitrite<-mean(bg_chem$NO2)
amm<-mean(bg_chem$NH4)
phos<-mean(bg_chem$P)
```


## c.Plot Redfield ratio
```{r}
ratio<-(nitrate+nitrite+amm)/phos
```

Here is the ratio calculated: `r round(ratio)`

3.  Conclusion
